Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-29 main.tex
Rough small intro

\iftext
\IEEEauthorblockN{Leonidas Lampropoulos}
\IEEEauthorblockA{\textit{University of Maryland \bcp{right?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\author{\IEEEauthorblockN{Roberto Blanco}
\IEEEauthorblockA{\textit{\bcp{affiliation?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
\and
\IEEEauthorblockN{Benjamin C. Pierce}
\IEEEauthorblockA{\textit{University of Pennsylvania}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\IEEEauthorblockN{Andrew Tolmach}
\IEEEauthorblockA{\textit{Portland State University}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
}
\fi

@@

\bcp{How about coining the term ``lockstep noninterference'' and then saying
  that we study several variants...?}
\leo{Rough story of the paper based on the discussion at POPL:}
\begin{itemize}
\item Noninterference is a desirable security property: secret information
  does not affect pulbic outputs of systems.
\item Traditionally, it is expressed as a {\em hyperproperty}, a
  property over pairs of execution traces. \leo{Two machines, differ
    secret data, run, indist}
\item The two execution traces are allowed differ arbitrarily in their
  control flow: branching on secret data can cause the machines to follow
  different execution paths.
\item \leo{Why is that bad? Hard to test/visualize? Even though interesting and permissive?}
\item \leo{Where do we mention contours, if at all?}
\item 
\item In this paper we describe a restricted form of hyperproperties:
  lockstep-hyperproperties, where the two traces execute the same
  sequence of instructions.
\item This kind of hyperproperty is still of practical interest: we
  can use it to encode both taint tracking, heap safety, and stack
  safety as noninterference properties.
\item Intuitively, taint tracking enforces noninterference until the
  program branches on tainted data. Then all bets are off.
\item On the other hand, stack safety is a monitoring policy that can
  enforce this lockstepness.
\item By restricting the class of hyperproperties we care about, we
  are also able to give a pretty extensional characterization of
  well-bracketed classification and declassification: what is
  considered secret can change throughout the execution.
\item For example, stack safety caller/callee accessible data.  
\end{itemize}

Contributions:
\begin{itemize}
\item \leo{Something about lockstep-hyperproperties as an abstraction}
\item An extensional characterization of taint tracking.
\item A novel stack safety policy and property characterized as noninterference.
\item A testing framework for testing lockstep-hyperproperties (merge with 1?)  
\end{itemize}

>>>>

% I get a weird error, so I commented this out for now
%\iftext
%\IEEEauthorblockN{Leonidas Lampropoulos}
%\IEEEauthorblockA{\textit{University of Maryland}}
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID
%\and
%\author{\IEEEauthorblockN{Roberto Blanco}
%\IEEEauthorblockA{\textit{\bcp{affiliation?}}
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID
%}
%\and
%\IEEEauthorblockN{Benjamin C. Pierce}
%\IEEEauthorblockA{\textit{University of Pennsylvania}
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID
%  }
%\and
%\IEEEauthorblockN{Andrew Tolmach}
%\IEEEauthorblockA{\textit{Portland State University}
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID
%}
%}
%\fi

@@

{\em Hyperproperties}, i.e. properties of pairs\leo{sets?} of execution traces,
are the standard way of expressing security properties\cn. In
particular, {\em noninterference} is commonly phrased as such a
property: given two system states that seem identical to an observer
with low clearance, their execution traces should also be
indistinguishable\cn.

In this paper we focus on a well-behaved closed subset of
hyperproperties, where the execution traces remain in {\em lockstep}:
the traces execute identical sequences of instructions. While such
lockstep hyperproperties appear restrictive at first, they are still
of practical interest, as they will allow us to give an extensional
characterization of security policies such as taint tracking or stack
safety, which have been traditionally approached
intentionally. Moreover, this setting admits a principled treatment of
well-bracketed classification and declassification. Finally, a
fortunate side-effect is that because of the lockstep nature of the
execution traces, lockstep-hyperproperties are far easier to test than
their more general counterparts.

Our contributions are:
\begin{itemize}
\item We present a mathematical abstraction of a class of properties
  called {\em lockstep hyperproperties}, that allow for intuitive
  characterizations of interesting security policies.
\item We give an extensional characterization of taint tracking as
  lockstep-noninterference.
\item We introduce a novel stack safety property that allows for
  the notion of observability to change dynamically throughout
  execution.
\item We develop a testing framework for testing such
  lockstep-hyperproperties, implemented as a parametric co-processor
  for RISC-V.
\end{itemize}
